\documentclass[letterpaper,11pt]{article}

%%  Dimensions and URL
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

%%  Definitions
\renewcommand{\baselinestretch}{1.1}
\pagestyle{plain}


\begin{document}

\begin{center}
{\bfseries \LARGE Task 2 -- Java and Eclipse\\[8mm]}
\end{center}

\section{The Java Programming Language}

Java is an object-oriented computer programming language that is designed to have few implementation dependencies.
Java applications are often compiled to bytecode that can run on any Java virtual machine (JVM), regardless of the underlying computer architecture.
This language was originally developed by Sun Microsystems, which has since been acquired by \href{http://www.oracle.com}{Oracle Corporation}.
Sun eventually released most of its Java technologies under the GNU General Public License.

Java Platform, Standard Edition (Java SE) is employed to develop and deploy Java applications on mobiles, desktops, servers, and embedded environments.
The Java Runtime Environment (JRE) contains a Java virtual machine, along with a set of standard class libraries that implement the Java application programming interface (API).
The Java Development Kit (JDK) is a software development kit that contains the necessary tools for the writing and running of Java programs.

\subsection*{Action Items}

\begin{itemize}
\item \textbf{Download and Install:} Java SE 8 Update 31 (JRE and JDK). \\
\url{http://www.oracle.com/technetwork/java/javase/downloads/index.html}
\end{itemize}


\section{IntelliJ IDEA}

IntelliJ IDEA is a Java integrated development environment (IDE) for programming computer software.
It is developed by \href{https://www.jetbrains.com}{JetBrains}, and the Community Edition is available under the Apache~2 Licensed.

\subsection*{Action Items}

\begin{itemize}
\item \textbf{Read:} About IntelliJ IDEA. \\
\url{https://www.jetbrains.com/idea/}
\item \textbf{Download and Install:} IntelliJ IDEA. \\
\url{https://www.jetbrains.com/idea/}
\item \textbf{Watch and Complete:} Installation and Startup. \\
\url{https://www.jetbrains.com/idea/documentation/video-tutorials.jsp}
\end{itemize}


\end{document}

